\newif\ifvimbug
\vimbugfalse

\ifvimbug
\begin{document}
\fi

\exercise{Statistics Refresher}
 

\begin{questions}

%----------------------------------------------

\begin{question}{Expectation and Variance}{8}
Let $\Omega$ be a finite set and $P:\Omega\rightarrow\R$ a probability measure that (by definition) satisfies $P(\omega)\geq0$ for all $\omega\in\Omega$ and $\sum_{\omega\in\Omega}P(\omega)=1$. 
Let $f:\Omega\rightarrow\R$ be an arbitrary function on $\Omega$.

\textbf{1)} Write the definition of expectation and variance of $f$ and discuss if they are linear operators.

\textbf{2)} You are given a set of three dices $\{A,B,C\}$.
The following table describes the outcome of six rollouts for these dices, where each column shows the outcome of the respective dice. 
(Note: assume the dices are standard six-sided dices with values between 1-6)
\begin{equation*}
\begin{array}{r|cccccc}
    A & 4 & 4 & 2 & 4 & 1 & 1 \\
    \hline
    B & 3 & 6 & 3 & 3 & 4 & 3 \\
    \hline
    C & 5 & 5 & 2 & 1 & 1 & 1 
\end{array}
\end{equation*}
Estimate the expectation and the variance for each dice using unbiased estimators. (Show your computations).

\textbf{3)} According to the data, which of them is the ``most rigged''? Why?

\begin{answer}\end{answer}

\end{question}

%----------------------------------------------

\begin{question}{It is a Cold World}{7}
Consider the following three statements:
\\
a) A person with a cold has backpain $24\%$ of the time.
\\
b) $5\%$ of the world population has a cold.
\\
c) $12\%$ of those who do not have a cold, still have backpain.

\textbf{1)} Identify random variables from the statements above and define a unique symbol for each of them.\\
\textbf{2)} Define the domain of each random variable.\\
\textbf{3)} Represent the three statements above with your random variables.\\
\textbf{4)} If you suffer from backpain, what are the chances that you suffer from a cold? (Show all the intermediate steps.)

\begin{answer}\end{answer}

\end{question}


%----------------------------------------------

\begin{question}{Journey to THX1138}{10}
	After the success of the \href{http://rosetta.esa.int/}{Rosetta mission}, ESA decided to send a spaceship to rendezvous with the comet THX1138. 
	This spacecraft consists of four independent subsystems $A,B,C,D$. 
	Each subsystem has a probability of failing during the journey equal to $1/3$. 
	\\
	1) What is the probability of the spacecraft $S$ to be in working condition (i.e., all subsystems are operational at the same time) at the rendezvous?
	\\
	2) Given that the spacecraft $S$ is not operating properly, compute	analytically the probability that \textbf{only} subsystem $A$ has failed. 
	\\
	3) Instead of computing the probability analytically, do a simple simulation experiment and compare the result to the previous solution. 
	Include a snippet of your code. 
	\\
	4) An improved spacecraft version has been designed.
	The new spacecraft fails if the critical subsystem $A$ fails, or any two subsystems of the remaining $B,C,D$ fail. 
	What is the probability that \textbf{only} subsystem $A$ has failed, given that the spacecraft $S$ is failing? 
	
	
\begin{answer}\end{answer}
	
\end{question}


\end{questions}
